Pillar 2 - Topic Modeling

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd

## Ideal Number of Topics (RUN ON UM COMPUTER)

```{r controls}
my_control <- list(

@@

)
```

```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

```{r description topics, cache = TRUE}
start.time <- Sys.time()

@@

```{r overview topics, cache = TRUE}
start.time <- Sys.time()

>>>>

## Ideal Number of Topics (RUN ON UM COMPUTER)
To decide the number of topics to discover, we run (four) three different tests.

First we set the control for the test.
```{r controls}
my_control <- list(

@@

)
```
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

}
```
We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
```{r description topics, cache = TRUE}
start.time <- Sys.time()

@@

We run the test for overview, documeting its duration. 
```{r overview topics, cache = TRUE}
start.time <- Sys.time()
